---
title: "PPMx-common: ABCD-ADHD Real Data Results"
date: today
format:
  revealjs:
    theme: default
    slide-number: true
    chalkboard: false
    scrollable: true
    code-fold: true
    toc: true
    toc-location: left
    embed-resources: true
    smaller: true
execute:
  cache: false
  warning: false
  error: false
  fig-format: png
  fig-width: 12
  fig-height: 7
  dpi: 300
---

```{r}
#| echo: false
# Load libraries
library(tidyverse)
library(patchwork)
library(ggsci)
library(gt)
library(htmltools)
library(knitr)

# ── Publication-ready theme ──────────────────────────────
theme_pub <- theme_bw(base_size = 12) +
  theme(
    strip.background = element_rect(fill = "grey92", colour = NA),
    strip.text = element_text(face = "bold", size = 11),
    legend.position = "bottom",
    legend.key.size = unit(0.35, "cm"),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", size = 13),
    plot.subtitle = element_text(colour = "grey40", size = 10),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10)
  )
theme_set(theme_pub)
scale_fill_pub <- scale_fill_npg()
scale_color_pub <- scale_color_npg()
pal_balance <- c("Balanced" = "#4DBBD5", "Imbalanced" = "#E64B35")

# Read key result files
results_dir <- "output"
sampledDF <- read_csv("output/sampledDF.csv", show_col_types = FALSE)

# 08 outputs (combined5foldCV.csv)
cv_path <- "output/baselines/combined5foldCV.csv"
cv_results <- read_csv(cv_path, show_col_types = FALSE)

# Sex-stratified CV results
cv_female_path <- "output/baselines-female/combined5foldCV.csv"
cv_male_path <- "output/baselines-male/combined5foldCV.csv"
cv_female <- if (file.exists(cv_female_path)) read_csv(cv_female_path, show_col_types = FALSE) else tibble()
cv_male <- if (file.exists(cv_male_path)) read_csv(cv_male_path, show_col_types = FALSE) else tibble()

# Subject profiles (optional — output of 09-subjectProfiles, ~4h)
profDir <- "output/openTotal/subjectProfilesK5-v2"
read_or_empty <- function(path) {
  if (file.exists(path)) read_csv(path, show_col_types = FALSE) else tibble()
}
anchors    <- read_or_empty(file.path(profDir, "anchors.csv"))
Dbar_df    <- read_or_empty(file.path(profDir, "Dbar.csv"))
betaBar_df <- read_or_empty(file.path(profDir, "betaBar.csv"))
subjectPost <- read_or_empty(file.path(profDir, "subjectPostSummary.csv"))
has_profiles <- nrow(anchors) > 0

modelVars <- c("age", "female", "uPosUrg", "uLplanning", "uLpers", "uNegUrg", "bbRR", "bbFS", "bbSum")
covLabels <- c(
  age = "Age", female = "Female", uPosUrg = "Pos. Urgency", uLplanning = "Lack of Planning",
  uLpers = "Lack of Perseverance", uNegUrg = "Neg. Urgency", bbRR = "BAS Reward",
  bbFS = "BAS Fun Seeking", bbSum = "BIS Total"
)

cat("Data loaded successfully.\n")
cat("  Subjects:", nrow(sampledDF), "\n")
cat("  CV folds:", nrow(cv_results), "\n")
cat("  CV female folds:", nrow(cv_female), "\n")
cat("  CV male folds:", nrow(cv_male), "\n")
cat("  Profiles available:", has_profiles, "\n")
```

## Overview

PPMx-common is a Bayesian partition model applied to the **ABCD-ADHD** dataset (~`r nrow(sampledDF)` subjects) to identify heterogeneity in ADHD symptom trajectories. The primary analysis uses a combined shrunk estimator with **K=5** latent classes identified via SALSO Binder loss.

| Metric | Value |
|---|---|
| Total subjects | `r nrow(sampledDF)` |
| Latent classes (K) | 5 |
| Model variables | `r length(modelVars)` (age, female, 7 temperament/impulsivity) |
| Outcome | nTotal (neuropsychological performance composite) |
| CV folds | 5 |

```{r}
#| echo: false
# Key summary table
overview_tbl <- tibble(
  Metric = c("Total subjects", "Latent classes (K)", "Model variables", "Outcome"),
  Value = c(nrow(sampledDF), 5, length(modelVars), "nTotal (neuropsych)")
)
overview_tbl |> gt() |> tab_header(title = "Analysis Overview") |> fmt_number(decimals = 0)
```

## Subject Profiles — K=5 Heatmap

The figure below shows the **subject-level posterior deviations** (D_i = β_i − β*) for all 9 covariates, ordered by SALSO Binder partition with prototype anchors highlighted in gold.

```{r}
#| fig-width: 12
#| fig-height: 8
#| echo: false

# Read the heatmap image and display it
heatmap_path <- file.path(profDir, "heatmap_Dbar_all9.png")
if (file.exists(heatmap_path)) {
  include_graphics(heatmap_path)
} else {
  cat("Heatmap not found. Run 09-subjectProfiles-combinedShrunkK5.jl first.\n")
}
```

## SALSO Cluster Assignments

The table below shows the **prototype anchors** — the most stable subject within each SALSO cluster, along with their consistency scores and ADHD levels.

```{r}
#| echo: false
if (has_profiles) {
  anchors |>
    gt() |>
    tab_header(title = "Anchor Subjects (SALSO Binder, K=5)") |>
    fmt_number(columns = c("consistency", starts_with("age"), starts_with("u"), starts_with("bb"), starts_with("ADHD")), decimals = 2) |>
    opt_interactive(use_compact_mode = TRUE)
} else {
  cat("Anchor data not available (run 09-subjectProfiles first).\n")
}
```

## Covariate Distributions

Distribution of the 9 modeled covariates in the standardized ABCD sample.

```{r}
#| fig-width: 10
#| fig-height: 7
#| echo: false

covpath <- if (file.exists("output/covariateDist.png")) "output/covariateDist.png" else NULL
if (!is.null(covpath) && file.exists(covpath)) {
  include_graphics(covpath)
} else {
  cat("Covariate distribution figure not found. Run covariateDist-ABCD.R first.\n")
}
```

## Cross-Validation: 5-Fold OOS RMSE

Out-of-sample root mean squared error across 5 folds of the combined PPMx-common model.

```{r}
#| fig-width: 8
#| fig-height: 5
#| echo: false

cv_plot <- ggplot(cv_results, aes(x = factor(fold), y = rmse, fill = factor(fold))) +
    geom_violin(alpha = 0.6, linewidth = 0.5, draw_quantiles = c(0.25, 0.5, 0.75)) +
    stat_summary(fun = median, geom = "point", size = 2.5, color = "black") +
    geom_hline(yintercept = mean(cv_results$rmse), linetype = "dashed", color = "red", linewidth = 0.8) +
    scale_fill_manual(values = rep("#4DBBD5", 5)) +
    labs(x = "Fold", y = "OOS RMSE", title = "5-Fold Cross-Validation RMSE",
         subtitle = paste0("Mean RMSE = ", round(mean(cv_results$rmse), 3), "  (dashed red line)")) +
    scale_fill_pub + theme_bw(base_size = 11) + theme(legend.position = "none") +
    theme(strip.text = element_text(face = "bold"))
print(cv_plot)
ggsave("output/presentations/fig_cv_rmse.png", plot = cv_plot, width = 12, height = 6, dpi = 300)
```

```{r}
#| echo: false
# CV summary table
cv_summary <- cv_results |>
    summarise(Mean_RMSE = mean(rmse), SD_RMSE = sd(rmse), Min_RMSE = min(rmse), Max_RMSE = max(rmse)) |>
    gt() |>
    tab_header(title = "5-Fold CV Summary (Combined PPMx-common)") |>
    fmt_number(decimals = 3) |>
print(cv_summary)
```

## Sex-Stratified Cross-Validation

Out-of-sample RMSE across 5 folds for female-only and male-only PPMx-common models.

```{r}
#| fig-width: 10
#| fig-height: 5
#| echo: false

# Combine female and male CV results
cv_sex <- bind_rows(
  cv_female %>% mutate(sex = "Female"),
  cv_male %>% mutate(sex = "Male")
)

if (nrow(cv_sex) > 0) {
  cv_sex_plot <- ggplot(cv_sex, aes(x = factor(fold), y = rmse, fill = sex)) +
      geom_violin(alpha = 0.6, linewidth = 0.5, draw_quantiles = c(0.25, 0.5, 0.75), position = position_dodge(width = 0.8)) +
      stat_summary(fun = median, geom = "point", size = 2.5, color = "black", position = position_dodge(width = 0.8)) +
      geom_hline(data = cv_sex %>% group_by(sex) %>% summarise(mean_rmse = mean(rmse)),
                 aes(yintercept = mean_rmse, color = sex), linetype = "dashed", linewidth = 0.8) +
      scale_fill_manual(values = c("Female" = "#E64B35", "Male" = "#4DBBD5")) +
      scale_color_manual(values = c("Female" = "#E64B35", "Male" = "#4DBBD5")) +
      labs(x = "Fold", y = "OOS RMSE", title = "5-Fold Cross-Validation RMSE (Sex-Stratified)",
           subtitle = paste0("Female mean = ", round(mean(cv_female$rmse, na.rm = TRUE), 3),
                           ", Male mean = ", round(mean(cv_male$rmse, na.rm = TRUE), 3))) +
      scale_fill_pub + theme_bw(base_size = 11) + theme(legend.position = "bottom") +
      theme(strip.text = element_text(face = "bold"))
  print(cv_sex_plot)
  ggsave("output/presentations/fig_cv_rmse_sex.png", plot = cv_sex_plot, width = 12, height = 6, dpi = 300)
} else {
  cat("Sex-stratified CV data not found.\n")
}
```

```{r}
#| echo: false
# Sex-stratified CV summary table
if (nrow(cv_sex) > 0) {
  cv_sex_summary <- cv_sex |>
      group_by(sex) |>
      summarise(Mean_RMSE = mean(rmse), SD_RMSE = sd(rmse), Min_RMSE = min(rmse), Max_RMSE = max(rmse)) |>
      gt() |>
      tab_header(title = "5-Fold CV Summary (Sex-Stratified PPMx-common)") |>
      fmt_number(decimals = 3) |>
  print(cv_sex_summary)
}
```

## Model Comparison

Comparison of PPMx-common against standard PPMx, k-means, and DPM baselines on ARI (clustering recovery) and OOS RMSE (prediction).

```{r}
#| echo: false
# Model comparison table from 06-baselines output
baseline_path <- "output/baselines/frftotalComparison.csv"
all_baseline <- tibble()

if (file.exists(baseline_path)) {
  all_baseline <- read_csv(baseline_path, show_col_types = FALSE)
  if (nrow(all_baseline) > 0) {
    all_baseline |>
      gt() |>
      tab_header(title = "Baseline Comparison (Combined Sample)") |>
      fmt_number(decimals = 3)
  } else {
    cat("No baseline data found.\n")
  }
} else {
  cat("Baseline results not found. Run 06-baselines-ABCD.jl first.\n")
}
```

## Sex-Stratified Baseline Comparison

Baseline comparison (ARI, RMSE, LPS, nclusters) for female-only and male-only models.

```{r}
#| echo: false
# Sex-stratified baseline tables
baseline_female_path <- "output/baselines-female/frftotalComparison.csv"
baseline_male_path <- "output/baselines-male/frftotalComparison.csv"
baseline_female <- if (file.exists(baseline_female_path)) read_csv(baseline_female_path, show_col_types = FALSE) else tibble()
baseline_male <- if (file.exists(baseline_male_path)) read_csv(baseline_male_path, show_col_types = FALSE) else tibble()
```

### Female Baseline Comparison

```{r}
#| echo: false
if (nrow(baseline_female) > 0) {
  baseline_female |>
    gt() |>
    tab_header(title = "Baseline Comparison (Female Only)") |>
    fmt_number(decimals = 3)
} else {
  cat("Female baseline data not found. Run 06b-female-ABCD.jl first.\n")
}
```

### Male Baseline Comparison

```{r}
#| echo: false
if (nrow(baseline_male) > 0) {
  baseline_male |>
    gt() |>
    tab_header(title = "Baseline Comparison (Male Only)") |>
    fmt_number(decimals = 3)
} else {
  cat("Male baseline data not found. Run 06c-male-ABCD.jl first.\n")
}
```

## Combined Baseline Summary

```{r}
#| echo: false
# Combined sex-stratified summary
if (nrow(baseline_female) > 0 && nrow(baseline_male) > 0) {
  baseline_combined <- bind_rows(
    baseline_female %>% mutate(sex = "Female"),
    baseline_male %>% mutate(sex = "Male")
  ) %>%
    select(model, sex, trainARI, testARI, testRMSE, testLPS, nclusters)

  baseline_combined |>
    gt() |>
    tab_header(title = "Combined Baseline Summary (Sex-Stratified)") |>
    fmt_number(decimals = 3) |>
    tab_spanner(label = "Train", columns = c(trainARI)) |>
    tab_spanner(label = "Test", columns = c(testARI, testRMSE, testLPS))
} else {
  cat("Sex-stratified baseline data not available.\n")
}
```

```{r}
#| echo: false
# Plot: test ARI vs RMSE by sex
if (nrow(baseline_female) > 0 && nrow(baseline_male) > 0) {
  baseline_combined <- bind_rows(
    baseline_female %>% mutate(sex = "Female"),
    baseline_male %>% mutate(sex = "Male")
  ) %>%
    select(model, sex, trainARI, testARI, testRMSE, testLPS, nclusters)

  ari_rmse_plot <- ggplot(baseline_combined, aes(x = testARI, y = testRMSE, color = sex, shape = model)) +
      geom_point(size = 4, alpha = 0.8) +
      scale_color_manual(values = c("Female" = "#E64B35", "Male" = "#4DBBD5")) +
      labs(x = "Test ARI (vs FRF)", y = "Test RMSE",
           title = "Sex-Stratified Baseline Comparison: ARI vs RMSE",
           subtitle = "Each point = one model. Females = red, Males = blue.") +
      scale_fill_pub + theme_bw(base_size = 11) + theme(legend.position = "bottom") +
      theme(strip.text = element_text(face = "bold"))
  print(ari_rmse_plot)
  ggsave("output/presentations/fig_baseline_ari_rmse_sex.png", plot = ari_rmse_plot, width = 12, height = 6, dpi = 300)
}
```

## Sex-Stratified Model Fit Comparison

Comprehensive model fit comparison across combined, female-only, and male-only samples. Includes testRMSE, testLPS, testARI, SALSO Binder/VI ARI, and 5-fold CV RMSE.

```{r}
#| echo: false
mfit_path <- "output/sexStratifiedMfit/mfit_comparison.csv"
deltas_path <- "output/sexStratifiedMfit/mfit_deltas.csv"

if (file.exists(mfit_path)) {
  mfit <- read_csv(mfit_path, show_col_types = FALSE)
  if (nrow(mfit) > 0) {
    mfit |>
      gt() |>
      tab_header(title = "Model Fit Comparison: Combined vs Female vs Male") |>
      fmt_number(decimals = 4)
  }
} else {
  cat("Model fit comparison not found. Run compareSexStratified-Mfit.R first.\n")
}
```

```{r}
#| echo: false
if (file.exists(deltas_path)) {
  deltas <- read_csv(deltas_path, show_col_types = FALSE)
  if (nrow(deltas) > 0) {
    deltas |>
      gt() |>
      tab_header(title = "Model Fit Deltas vs Combined (▲ better, ▼ worse)") |>
      fmt_number(decimals = 4)
  }
} else {
  cat("Deltas not found.\n")
}
```

### Test RMSE by Sample

```{r}
#| fig-width: 10
#| fig-height: 6
#| echo: false
rmse_fig <- "output/sexStratifiedMfit/fig_rmse.png"
if (file.exists(rmse_fig)) {
  knitr::include_graphics(rmse_fig)
} else {
  cat("RMSE figure not found.\n")
}
```

### Test LPS by Sample

```{r}
#| fig-width: 10
#| fig-height: 6
#| echo: false
lps_fig <- "output/sexStratifiedMfit/fig_lps.png"
if (file.exists(lps_fig)) {
  knitr::include_graphics(lps_fig)
} else {
  cat("LPS figure not found.\n")
}
```

### ARI Family by Sample

```{r}
#| fig-width: 14
#| fig-height: 5
#| echo: false
ari_fig <- "output/sexStratifiedMfit/fig_ari.png"
if (file.exists(ari_fig)) {
  knitr::include_graphics(ari_fig)
} else {
  cat("ARI figure not found.\n")
}
```

### 5-Fold CV RMSE by Sample

```{r}
#| fig-width: 10
#| fig-height: 6
#| echo: false
cv_fig <- "output/sexStratifiedMfit/fig_cv_fold.png"
if (file.exists(cv_fig)) {
  knitr::include_graphics(cv_fig)
} else {
  cat("CV fold figure not found.\n")
}
```

## Subject-Level Posterior Summaries

Quantile summaries (5th, 50th, 95th percentiles) of the D_i posterior for each subject × covariate combination.

```{r}
#| echo: false
if (nrow(subjectPost) > 0) {
  # Show first 20 rows
  subjectPost |>
    head(20) |>
    gt() |>
    tab_header(title = "Subject Posterior Summaries (first 20 rows)") |>
    fmt_number(decimals = 3)
} else {
  cat("Subject posterior summaries not found.\n")
}
```

```{r}
#| echo: false
if (nrow(subjectPost) > 0) {
  cat("\nTotal rows:", nrow(subjectPost), "\n")
  cat("Unique subjects:", length(unique(subjectPost$IID)), "\n")
}
```

## Anchor Profiles by Covariate

Posterior mean deviation (Dbar) for each anchor subject across the 9 covariates, faceted by SALSO cluster.

```{r}
#| fig-width: 10
#| fig-height: 6
#| echo: false

if (nrow(anchors) > 0 && nrow(Dbar_df) > 0) {
  # Standardize each covariate (z-score across all anchors) so profiles share an axis,
  # then filter to the 10-90 percentile range to reduce outlier influence
  anchor_long <- anchors |>
    pivot_longer(cols = all_of(modelVars), names_to = "covariate", values_to = "Dbar") |>
    mutate(covariate = factor(covariate, levels = modelVars, labels = covLabels[modelVars]),
           salso = factor(salso)) |>
    group_by(covariate) |>
    mutate(zDbar = (Dbar - mean(Dbar, na.rm = TRUE)) / sd(Dbar, na.rm = TRUE)) |>
    ungroup() |>
    group_by(covariate) |>
    filter(zDbar >= quantile(zDbar, 0.1, na.rm = TRUE) &
           zDbar <= quantile(zDbar, 0.9, na.rm = TRUE)) |>
    ungroup()

  anchor_plot <- anchor_long |>
    ggplot(aes(x = covariate, y = zDbar, fill = salso)) +
    geom_violin(alpha = 0.55, linewidth = 0.4) +
    stat_summary(fun = median, geom = "point", size = 1.5, color = "black", position = position_dodge(width = 0.8)) +
    labs(x = "Covariate", y = expression(paste("Standardized ", Dbar)),
         fill = "SALSO Cluster",
         title = "Anchor Subject Profile Deviations (standardized, 10-90% range)") +
    scale_fill_pub + theme_bw(base_size = 10) + theme(legend.position = "bottom",
      axis.text.x = element_text(size = 8, angle = 30, hjust = 1))
  ggsave("output/presentations/fig_anchor_profiles.png", plot = anchor_plot, width = 14, height = 6, dpi = 300)
  print(anchor_plot)
} else {
  cat("Anchor data not found.\n")
}
```

## SALSO Binder Loss Diagnostics

Distribution of SALSO Binder and VI loss ARI values across the posterior draws.

```{r}
#| echo: false
# Check if SALSO results are available from the baselines
salso_cols <- c("salsoBinderARI_Mix", "salsoVIARI_Mix", "salsoBinderARI_Mixoos", "salsoVIARI_Mixoos")
if (nrow(all_baseline) > 0 && any(salso_cols %in% names(all_baseline))) {
  salso_long <- all_baseline |>
    select(any_of(salso_cols)) |>
    pivot_longer(everything(), names_to = "metric", values_to = "ARI") |>
    mutate(metric = recode(metric,
      "salsoBinderARI_Mix" = "Binder (in-sample)",
      "salsoVIARI_Mix" = "VI (in-sample)",
      "salsoBinderARI_Mixoos" = "Binder (OOS)",
      "salsoVIARI_Mixoos" = "VI (OOS)"))

  p_salso <- salso_long |>
    ggplot(aes(x = metric, y = ARI, fill = metric)) +
    geom_violin(alpha = 0.6, linewidth = 0.5) +
    stat_summary(fun = median, geom = "point", size = 2, color = "black") +
    labs(x = "Method", y = "Adjusted Rand Index", title = "SALSO Point Estimate Diagnostics",
         subtitle = "ARI vs truth. Median indicated.") +
    scale_fill_pub + theme_bw(base_size = 11) + theme(legend.position = "none") +
    theme(axis.text.x = element_text(size = 9))
  print(p_salso)
  ggsave("output/presentations/fig_salso_diag.png", plot = p_salso, width = 12, height = 5, dpi = 300)
} else {
  cat("SALSO ARI columns not found in baseline data.\n")
  cat("Ensure 06-baselines-ABCD.jl runs with RCall + salso available.\n")
}
```

## Posterior Predictive Checks

Posterior predictive distributions for the outcome (nTotal) across subjects, stratified by SALSO cluster.

```{r}
#| echo: false
# Check if betaBar is available for posterior predictive checks
if (nrow(betaBar_df) > 0) {
  betaBar_plot <- betaBar_df |>
    pivot_longer(cols = all_of(modelVars), names_to = "covariate", values_to = "beta") |>
    mutate(covariate = factor(covariate, levels = modelVars, labels = covLabels[modelVars])) |>
    group_by(covariate) |>
    filter(beta >= quantile(beta, 0.1, na.rm = TRUE) &
           beta <= quantile(beta, 0.9, na.rm = TRUE)) |>
    ungroup() |>
    ggplot(aes(x = salso, y = beta, fill = factor(salso))) +
    geom_violin(alpha = 0.55, linewidth = 0.4) +
    stat_summary(fun = median, geom = "point", size = 1.5, color = "black") +
    facet_wrap(~covariate, scales = "free", ncol = 3) +
    labs(x = "SALSO Cluster", y = expression(beta[posterior]), fill = "Cluster",
         title = "Posterior Beta Distributions by SALSO Cluster") +
    scale_fill_pub + theme_bw(base_size = 10) + theme(legend.position = "none")
  print(betaBar_plot)
  ggsave("output/presentations/fig_posterior_beta.png", plot = betaBar_plot, width = 12, height = 6, dpi = 300)

  # Posterior predictive: predicted nTotal per SALSO cluster
  # Computed via ProductPartitionModels.postPred on held-out test set
  postPred_path <- "output/openTotal/subjectProfilesK5-v2/postPred.csv"
  postPred_df <- if (file.exists(postPred_path)) {
    read_csv(postPred_path, show_col_types = FALSE)
  } else {
    tibble()
  }

  if (nrow(postPred_df) > 0) {
    postPred_df <- postPred_df |>
      mutate(salso = factor(salso)) |>
      group_by(salso) |>
      filter(nTotal_pred >= quantile(nTotal_pred, 0.1, na.rm = TRUE) &
             nTotal_pred <= quantile(nTotal_pred, 0.9, na.rm = TRUE)) |>
      ungroup()

    p_ntotal <- postPred_df |>
      ggplot(aes(x = salso, y = nTotal_pred, fill = salso)) +
      geom_violin(alpha = 0.6, linewidth = 0.5) +
      stat_summary(fun = median, geom = "point", size = 2.5, color = "black") +
      geom_hline(yintercept = 0, linetype = "dashed", color = "grey40") +
      scale_fill_pub + theme_bw(base_size = 11) + theme(legend.position = "none") +
      labs(x = "SALSO Cluster", y = "Predicted nTotal",
           title = "Posterior Predictive: Outcome Distribution per SALSO Cluster",
           subtitle = "Violin of postPred nTotal per SALSO cluster (held-out test set)")
    print(p_ntotal)
    ggsave("output/presentations/fig_predictive_ntotal.png", plot = p_ntotal, width = 10, height = 6, dpi = 300)
  } else {
    cat("postPred data not found. Run 09-subjectProfiles first.\n")
  }
}
```

## Appendix: Complete Results Tables

### All Anchor Subjects

```{r}
#| echo: false
if (nrow(anchors) > 0) {
  anchors |>
    gt() |>
    tab_header(title = "All Anchor Subjects (K=5)") |>
    fmt_number(decimals = 3)
}
```

### Subject Posterior Summary (All Subjects)

```{r}
#| echo: false
#| column: page
if (nrow(subjectPost) > 0) {
  # Aggregate by covariate
  agg <- subjectPost |>
    group_by(covariate, salso) |>
    summarise(
      mean_q50 = mean(q50, na.rm = TRUE),
      mean_q05 = mean(q05, na.rm = TRUE),
      mean_q95 = mean(q95, na.rm = TRUE),
      mean_mean = mean(mean, na.rm = TRUE),
      .groups = "drop"
    ) |>
    gt() |>
    tab_header(title = "Subject Posterior Summary by Covariate and Cluster") |>
    fmt_number(decimals = 3)
}
```

### 5-Fold CV Details

```{r}
#| echo: false
cv_results |>
    gt() |>
    tab_header(title = "5-Fold CV: Fold-level RMSE") |>
    fmt_number(decimals = 4) 
```

<!-- -->

## Reproducibility

All analyses were run using:
- **Julia 1.11.7** with `ProductPartitionModels.jl` (v2.0 branch)
- **R** with `tidyverse`, `ggplot2`, `patchwork`, `ggsci`, `gt`, `quarto`
- Environment: `ProductPartitionModels.jl/simulations/`
- Scripts: `ppmx-analysis/analyses/`
- Data: ABCD-ADHD (downloaded from ABCD archive)

To reproduce:
```bash
cd ~/papers/ABCD-adhd/analyses
sbatch runAllRealData.sh
quarto render vizReal.qmd --to revealjs --output-dir output/presentations
```
