---
title: "PPMx-common: ABCD-ADHD Real Data Results"
date: today
format:
  revealjs:
    theme: default
    slide-number: true
    chalkboard: false
    scrollable: true
    code-fold: true
    toc: true
    toc-location: left
    embed-resources: true
    smaller: true
execute:
  cache: false
  warning: false
  error: false
  fig-format: png
  fig-width: 10
  fig-height: 6
---

```{r}
#| echo: false
# Load libraries
library(tidyverse)
library(patchwork)
library(ggsci)
library(gt)
library(htmltools)

theme_set(theme_bw())
theme_update(
  scale_fill = scale_fill_npg(),
  scale_color = scale_color_npg(),
)

# ── Helper functions ──────────────────────────────────────────────────────
gt_scroll <- function(gt_tbl, max_h = "500px") {
  htmltools::div(style = sprintf("overflow-x:auto; overflow-y:auto; max-height:%s; border:1px solid #ddd; padding:4px;", max_h), gt_tbl)
}

# Read key result files
results_dir <- "output"
sampledDF <- read_csv("output/sampledDF.csv", show_col_types = FALSE)
# 08 outputs are optional (48h refit); downstream chunks already guard on
# nrow(cv_results) > 0, so default to an empty tibble when the file is absent.
cv_path <- "output/baselines/combined5foldCV.csv"
cv_results <- if (file.exists(cv_path)) {
  read_csv(cv_path, show_col_types = FALSE)
} else {
  tibble()
}

# Subject profiles (optional — output of 09-subjectProfiles, ~4h)
profDir <- "output/openTotal/subjectProfilesK5-v2"
read_or_empty <- function(path) {
  if (file.exists(path)) read_csv(path, show_col_types = FALSE) else tibble()
}
anchors    <- read_or_empty(file.path(profDir, "anchors.csv"))
Dbar_df    <- read_or_empty(file.path(profDir, "Dbar.csv"))
betaBar_df <- read_or_empty(file.path(profDir, "betaBar.csv"))
subjectPost <- read_or_empty(file.path(profDir, "subjectPostSummary.csv"))
has_profiles <- nrow(anchors) > 0

modelVars <- c("age", "female", "uPosUrg", "uLplanning", "uLpers", "uNegUrg", "bbRR", "bbFS", "bbSum")
covLabels <- c(
  age = "Age", female = "Female", uPosUrg = "Pos. Urgency", uLplanning = "Lack of Planning",
  uLpers = "Lack of Perseverance", uNegUrg = "Neg. Urgency", bbRR = "BAS Reward",
  bbFS = "BAS Fun Seeking", bbSum = "BIS Total"
)

cat("Data loaded successfully.\n")
cat("  Subjects:", nrow(sampledDF), "\n")
cat("  CV folds:", nrow(cv_results), "\n")
cat("  Profiles available:", has_profiles, "\n")
```

## Overview

PPMx-common is a Bayesian partition model applied to the **ABCD-ADHD** dataset (~`r nrow(sampledDF)` subjects) to identify heterogeneity in ADHD symptom trajectories. The primary analysis uses a combined shrunk estimator with **K=5** latent classes identified via SALSO Binder loss.

| Metric | Value |
|---|---|
| Total subjects | `r nrow(sampledDF)` |
| Latent classes (K) | 5 |
| Model variables | `r length(modelVars)` (age, female, 7 temperament/impulsivity) |
| Outcome | nTotal (neuropsychological performance composite) |
| CV folds | 5 |

```{r}
#| echo: false
# Key summary table
overview_tbl <- tibble(
  Metric = c("Total subjects", "Latent classes (K)", "Model variables", "Outcome"),
  Value = c(nrow(sampledDF), 5, length(modelVars), "nTotal (neuropsych)")
)
overview_tbl |> gt() |> tab_header(title = "Analysis Overview") |> fmt_number(decimals = 0)
```

## Subject Profiles — K=5 Heatmap

The figure below shows the **subject-level posterior deviations** (D_i = β_i − β*) for all 9 covariates, ordered by SALSO Binder partition with prototype anchors highlighted in gold.

```{r}
#| fig-width: 12
#| fig-height: 8
#| echo: false

# Read the heatmap image and display it
heatmap_path <- file.path(profDir, "heatmap_Dbar_all9.png")
if (file.exists(heatmap_path)) {
  include_graphics(heatmap_path)
} else {
  cat("Heatmap not found. Run 09-subjectProfiles-combinedShrunkK5.jl first.\n")
}
```

## SALSO Cluster Assignments

The table below shows the **prototype anchors** — the most stable subject within each SALSO cluster, along with their consistency scores and ADHD levels.

```{r}
#| echo: false
if (has_profiles) {
  anchors |>
    gt() |>
    tab_header(title = "Anchor Subjects (SALSO Binder, K=5)") |>
    fmt_number(columns = c("consistency", starts_with("age"), starts_with("u"), starts_with("bb"), starts_with("ADHD")), decimals = 2) |>
    opt_interactive(use_compact_mode = TRUE) |>
    gt_scroll()
} else {
  cat("Anchor data not available (run 09-subjectProfiles first).\n")
}
```

## Covariate Distributions

Distribution of the 9 modeled covariates in the standardized ABCD sample.

```{r}
#| fig-width: 10
#| fig-height: 7
#| echo: false

covpath <- if (file.exists("output/covariateDist.png")) "output/covariateDist.png" else NULL
if (!is.null(covpath) && file.exists(covpath)) {
  include_graphics(covpath)
} else {
  cat("Covariate distribution figure not found. Run covariateDist-ABCD.R first.\n")
}
```

## Cross-Validation: 5-Fold OOS RMSE

Out-of-sample root mean squared error across 5 folds of the combined PPMx-common model.

```{r}
#| fig-width: 8
#| fig-height: 5
#| echo: false

if (nrow(cv_results) > 0) {
  cv_plot <- ggplot(cv_results, aes(x = factor(fold), y = rmse)) +
    geom_bar(stat = "identity", fill = "#4DBBD5", color = "white") +
    geom_hline(yintercept = mean(cv_results$rmse), linetype = "dashed", color = "red", linewidth = 1) +
    labs(x = "Fold", y = "OOS RMSE", title = "5-Fold Cross-Validation RMSE",
         subtitle = paste0("Mean RMSE = ", round(mean(cv_results$rmse), 3))) +
    theme_bw(base_size = 12)
  print(cv_plot)
} else {
  cat("CV results not found.\n")
}
```

```{r}
#| echo: false
# CV summary table
if (nrow(cv_results) > 0) {
  cv_summary <- cv_results |>
    summarise(Mean_RMSE = mean(rmse), SD_RMSE = sd(rmse), Min_RMSE = min(rmse), Max_RMSE = max(rmse)) |>
    gt() |>
    tab_header(title = "5-Fold CV Summary (Combined PPMx-common)") |>
    fmt_number(decimals = 3) |>
    gt_scroll()
  print(cv_summary)
}
```

## Model Comparison

Comparison of PPMx-common against standard PPMx, k-means, and DPM baselines on ARI (clustering recovery) and OOS RMSE (prediction).

```{r}
#| echo: false
# Model comparison table from 06-baselines output
baselines_dir <- "output/baselines"
baseline_files <- list.files(baselines_dir, pattern = "\\.csv$", full.names = TRUE)
all_baseline <- tibble()

if (length(baseline_files) > 0) {
  all_baseline <- map_dfr(baseline_files, read_csv, show_col_types = FALSE)
  if (nrow(all_baseline) > 0) {
    all_baseline |>
      gt() |>
      tab_header(title = "Baseline Comparison (all outcomes)") |>
      fmt_number(decimals = 3) |>
      gt_scroll()
  } else {
    cat("No baseline data found.\n")
  }
} else {
  cat("Baseline results not found. Run 06-baselines-ABCD.jl first.\n")
}
```

## Subject-Level Posterior Summaries

Quantile summaries (5th, 50th, 95th percentiles) of the D_i posterior for each subject × covariate combination.

```{r}
#| echo: false
if (nrow(subjectPost) > 0) {
  # Show first 20 rows
  subjectPost |>
    head(20) |>
    gt() |>
    tab_header(title = "Subject Posterior Summaries (first 20 rows)") |>
    fmt_number(decimals = 3) |>
    gt_scroll()

  cat("\nTotal rows:", nrow(subjectPost), "\n")
  cat("Unique subjects:", length(unique(subjectPost$IID)), "\n")
} else {
  cat("Subject posterior summaries not found.\n")
}
```

## Anchor Profiles by Covariate

Posterior mean deviation (Dbar) for each anchor subject across the 9 covariates, faceted by SALSO cluster.

```{r}
#| fig-width: 10
#| fig-height: 6
#| echo: false

if (nrow(anchors) > 0 && nrow(Dbar_df) > 0) {
  anchor_plot <- anchors |>
    pivot_longer(cols = all_of(modelVars), names_to = "covariate", values_to = "Dbar") |>
    mutate(covariate = factor(covariate, levels = modelVars, labels = covLabels[modelVars])) |>
    ggplot(aes(x = salso, y = Dbar, fill = factor(salso))) +
    geom_bar(stat = "identity", position = position_dodge()) +
    facet_wrap(~covariate, scales = "free", ncol = 3) +
    labs(x = "SALSO Cluster", y = "Dbar (β_anchor − β*)", fill = "Cluster") +
    scale_fill_npg() + theme_bw(base_size = 10) + theme(legend.position = "none") +
    ggtitle("Anchor Subject Profile Deviations by SALSO Cluster")
  print(anchor_plot)
} else {
  cat("Anchor data not found.\n")
}
```

## SALSO Binder Loss Diagnostics

Distribution of SALSO Binder and VI loss ARI values across the posterior draws.

```{r}
#| echo: false
# Check if SALSO results are available from the baselines
salso_cols <- c("salsoBinderARI_Mix", "salsoVIARI_Mix", "salsoBinderARI_Mixoos", "salsoVIARI_Mixoos")
if (nrow(all_baseline) > 0 && any(salso_cols %in% names(all_baseline))) {
  salso_long <- all_baseline |>
    select(any_of(salso_cols)) |>
    pivot_longer(everything(), names_to = "metric", values_to = "ARI") |>
    mutate(metric = recode(metric,
      "salsoBinderARI_Mix" = "Binder (in-sample)",
      "salsoVIARI_Mix" = "VI (in-sample)",
      "salsoBinderARI_Mixoos" = "Binder (OOS)",
      "salsoVIARI_Mixoos" = "VI (OOS)"))

  salso_long |>
    ggplot(aes(x = ARI, fill = metric)) +
    geom_density(alpha = 0.4) +
    facet_wrap(~metric, scales = "free_x") +
    labs(x = "SALSO ARI", y = "Density", title = "SALSO Point Estimate Diagnostics") +
    scale_fill_npg() + theme_bw()
} else {
  cat("SALSO ARI columns not found in baseline data.\n")
  cat("Ensure 06-baselines-ABCD.jl runs with RCall + salso available.\n")
}
```

## Posterior Predictive Checks

Posterior predictive distributions for the outcome (nTotal) across subjects, stratified by SALSO cluster.

```{r}
#| echo: false
# Check if betaBar is available for posterior predictive checks
if (nrow(betaBar_df) > 0) {
  betaBar_df |>
    pivot_longer(cols = all_of(modelVars), names_to = "covariate", values_to = "beta") |>
    mutate(covariate = factor(covariate, levels = modelVars, labels = covLabels[modelVars])) |>
    ggplot(aes(x = beta, fill = factor(salso))) +
    geom_density(alpha = 0.4) +
    facet_wrap(~covariate, scales = "free", ncol = 3) +
    labs(x = "Posterior Mean β_i", fill = "SALSO Cluster", title = "Posterior Beta Distributions by Cluster") +
    scale_fill_npg() + theme_bw()
} else {
  cat("betaBar data not found.\n")
}
```

## Appendix: Complete Results Tables

### All Anchor Subjects

```{r}
#| echo: false
if (nrow(anchors) > 0) {
  anchors |>
    gt() |>
    tab_header(title = "All Anchor Subjects (K=5)") |>
    fmt_number(decimals = 3) |>
    gt_scroll()
}
```

### Subject Posterior Summary (All Subjects)

```{r}
#| echo: false
#| column: page
if (nrow(subjectPost) > 0) {
  # Aggregate by covariate
  agg <- subjectPost |>
    group_by(covariate, salso) |>
    summarise(
      mean_q50 = mean(q50, na.rm = TRUE),
      mean_q05 = mean(q05, na.rm = TRUE),
      mean_q95 = mean(q95, na.rm = TRUE),
      mean_mean = mean(mean, na.rm = TRUE),
      .groups = "drop"
    ) |>
    gt() |>
    tab_header(title = "Subject Posterior Summary by Covariate and Cluster") |>
    fmt_number(decimals = 3) |>
    gt_scroll()
}
```

### 5-Fold CV Details

```{r}
#| echo: false
if (nrow(cv_results) > 0) {
  cv_results |>
    gt() |>
    tab_header(title = "5-Fold CV: Fold-level RMSE") |>
    fmt_number(decimals = 4) |>
    gt_scroll()
}
```

<!-- -->

## Reproducibility

All analyses were run using:
- **Julia 1.11.7** with `ProductPartitionModels.jl` (v2.0 branch)
- **R** with `tidyverse`, `ggplot2`, `patchwork`, `ggsci`, `gt`, `quarto`
- Environment: `ProductPartitionModels.jl/simulations/`
- Scripts: `ppmx-analysis/analyses/`
- Data: ABCD-ADHD (downloaded from ABCD archive)

To reproduce:
```bash
cd ~/papers/ABCD-adhd/analyses
sbatch runAllRealData.sh
quarto render vizReal.qmd --to revealjs --output-dir output/presentations
```
